Supporting Information for RIVER NETWORKS DAMPEN LONG-TERM HYRDOLOGICAL SIGNALS OF CLIMATE CHANGE.

### 2017-05-31 drafts/AGU_Journal/submission 2/ms_Geo_Let_SI.tex
Added timber harvest data reference.
Small manuscript updates to meet the requirments of the reviewer

	The following supplementary material includes 8 additional figures. Figures~\ref{fig:S1}, \ref{fig:S2}, \ref{fig:S3} and \ref{fig:S8} explore the impact of timber harvest on flow in the Fraser River basin in British Columbia, CA. These figures aim to demonstrate the complicated and unclear relationship between flow trends and forest cover change. Figures \ref{fig:S6} and \ref{fig:S7} are similar to figure 4 in the main text where monthly flow trends in the Fraser River basin are shown along with trend attenuation results. These supplementary figures highlight minimum and median seasonal flow trends rather than maximum seasonal flow trends. Figures \ref{fig:S4} and \ref{fig:S5} are example plots demonstrating a single null-model iteration for the median flow metric.

@@

\begin{figure}[h]
	\centering
	\setfigurenum{S6}
	\noindent\includegraphics[width=35pc]{FigS6_MinMonth.pdf}
	\caption{Monthly minimum flow trend attenuation within the Fraser River basin. (\textbf{Left}) Fraser River's basin-wide minimum-flow trend estimates (i.e., intercept = vertical grey lines) by month with density distributions of null-model simulations. Observed values falling further from the center of the density distribution suggest greater evidence for changes in minimum flow and a greater shift in magnitude. (\textbf{Center}) Observed monthly Fraser River minimum-flow variance exponent ($\hat{\updelta}$, blue) and associated density distribution of simulated $\hat{\updelta}$ estimates. Decimal values represent the percent of simulated data exhibiting weaker attenuation (yellow) than observed. (\textbf{Right}) Trend estimates $\pm$ one standard error (SE, grey) plotted against watershed area (km\textsuperscript{2}), colored by climate portfolio strength (green = small, blue = large), for four seasonally representative months. These reflect months in the prior columns and describe the variation in percent change per decade of minimum flow among sites. Simulated lines ignore variance in the intercept and slope to focus visually on attenuation.}
	\label{fig:S6}
\end{figure}

\begin{figure}[h]
	\centering
	\setfigurenum{S7}
	\noindent\includegraphics[width=35pc]{FigS7_MedMonth.pdf}
	\caption{Monthly median flow trend attenuation within the Fraser River basin. (\textbf{Left}) Fraser River's basin-wide median-flow trend estimates (i.e., intercept = vertical grey lines) by month with density distributions of null-model simulations. Observed values falling further from the center of the density distribution suggest greater evidence for changes in median flow and a greater shift in magnitude. (\textbf{Center}) Observed monthly Fraser River median-flow variance exponent ($\hat{\updelta}$, blue) and associated density distribution of simulated $\hat{\updelta}$ estimates. Decimal values represent the percent of simulated data exhibiting weaker attenuation (yellow) than observed. (\textbf{Right}) Trend estimates $\pm$ one standard error (SE, grey) plotted against watershed area (km\textsuperscript{2}), colored by climate portfolio strength (green = small, blue = large),for four seasonally representative months. These reflect months in the prior columns and describe the variation in percent change per decade of median flow among sites. Simulated lines ignore variance in the intercept and slope to focus visually on attenuation.}
	\label{fig:S7}
\end{figure}

>>>>

	The following supplementary material includes 8 additional figures. Figures~\ref{fig:S1}, \ref{fig:S2}, \ref{fig:S3} and \ref{fig:S8} explore the impact of timber harvest on flow in the Fraser River basin in British Columbia, CA. These figures aim to demonstrate the complicated and unclear relationship between flow trends and forest cover change. Timber harvest data were obtained through British Columbia's Forest Practices Board, based on the Vegitation Resources Inventory (VRI) (\url{http:www.for.gov.bc.ca/hts/vri/}). Figures \ref{fig:S6} and \ref{fig:S7} are similar to figure 4 in the main text where monthly flow trends in the Fraser River basin are shown along with trend attenuation results. These supplementary figures highlight minimum and median seasonal flow trends rather than maximum seasonal flow trends. Figures \ref{fig:S4} and \ref{fig:S5} are example plots demonstrating a single null-model iteration for the median flow metric.

@@

\begin{figure}[h]
	\centering
	\setfigurenum{S6}
	\noindent\includegraphics[width=35pc]{FigS6_MinMonth.pdf}
	\caption{Monthly minimum flow trend attenuation within the Fraser River basin. (\textbf{Left}) Fraser River's basin-wide minimum-flow trend estimates (i.e., intercept = vertical grey lines) by month with density distributions of null-model simulations. Observed values falling further from the center of the density distribution suggest greater evidence for changes in minimum flow and a greater shift in magnitude. (\textbf{Center}) Observed monthly Fraser River minimum-flow variance exponent ($\hat{\updelta}$, blue) and associated density distribution of simulated $\hat{\updelta}$ estimates. Decimal values represent the percent of simulated data exhibiting weaker attenuation (yellow) than observed. (\textbf{Right}) Trend estimates ($\hat{b}_{s}$) $\pm$ one standard error (SE, grey) plotted against watershed area (km\textsuperscript{2}), colored by climate portfolio strength (green = small, blue = large), for four seasonally representative months. These reflect months in the prior columns and describe the variation in percent change per decade of minimum flow among sites. Simulated lines ignore variance in the intercept and slope to focus visually on attenuation.}
	\label{fig:S6}
\end{figure}

\begin{figure}[h]
	\centering
	\setfigurenum{S7}
	\noindent\includegraphics[width=35pc]{FigS7_MedMonth.pdf}
	\caption{Monthly median flow trend attenuation within the Fraser River basin. (\textbf{Left}) Fraser River's basin-wide median-flow trend estimates (i.e., intercept = vertical grey lines) by month with density distributions of null-model simulations. Observed values falling further from the center of the density distribution suggest greater evidence for changes in median flow and a greater shift in magnitude. (\textbf{Center}) Observed monthly Fraser River median-flow variance exponent ($\hat{\updelta}$, blue) and associated density distribution of simulated $\hat{\updelta}$ estimates. Decimal values represent the percent of simulated data exhibiting weaker attenuation (yellow) than observed. (\textbf{Right}) Trend estimates ($\hat{b}_{s}$) $\pm$ one standard error (SE, grey) plotted against watershed area (km\textsuperscript{2}), colored by climate portfolio strength (green = small, blue = large), for four seasonally representative months. These reflect months in the prior columns and describe the variation in percent change per decade of median flow among sites. Simulated lines ignore variance in the intercept and slope to focus visually on attenuation.}
	\label{fig:S7}
\end{figure}
